---
title: "Home"
layout: default
---

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>"
)
```

```{r echo=FALSE}
# install pkgs if not installed already
invisible(lapply(c('magrittr', 'httr', 'rvest', 'cowsay'), function(x) {
  if (!requireNamespace(x, quietly = TRUE)) install.packages(x, quiet = TRUE)
}))
```

## An intro to APIs for R users

This is an introduction to working with APIs in R. I promise this will be fun. 

xxx

## Table of contents

* [Definitions](#definitions)
* [Server-Client](#serverclient)
* [URLs](#urls)
* [Install things](#install)
* [Your first GET request](#get)
* [Reading](#reading)
* [Does this site suck?](#makeitbetter)

## <a href="#definitions" name="definitions">#</a> Definitions

xxxx


## <a href="#serverclient" name="serverclient">#</a> Server-Client

xxxx

## <a href="#urls" name="urls">#</a> URLs

xxx

## <a href="#install" name="install">#</a> Install

xxx

## <a href="#get" name="get">#</a> Your first GET request

xxx

## <a href="#reading" name="reading">#</a> Reading

xxxx

## <a href="#makeitbetter" name="makeitbetter">#</a> Make it better

Contribute by following [these instructions](/Contribute).

## <a href="#license" name="license">#</a> License
